Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-04 sections/appendix.tex
reorg
need to edit contributions

\section{Graph Algorithms}

\subsection{Finch Breadth-First Search}
\begin{minted}{julia}
    function bfs_finch_kernel(edges, edgesT, source=5, alpha = 0.01)
    (n, m) = size(edges)
    edges = pattern!(edges)
    @assert n == m
    F = Tensor(SparseByteMap(Pattern()), n)
    _F = Tensor(SparseByteMap(Pattern()), n)
    @finch F[source] = true
    F_nnz = 1 
    V = Tensor(Dense(Element(false)), n)
    @finch V[source] = true
    P = Tensor(Dense(Element(0)), n)
    @finch P[source] = source
    while F_nnz > 0 
        if F_nnz/m > alpha # pull
            p = ShortCircuitScalar{0}()
            _F .= false
            for k=_ 
                if !V[k]
                    p .= 0
                    for j=_ 
                        if F[follow(j)] && AT[j, k]
                            p[] <<choose(0)>>= j
                        end 
                    end 
                    if p[] != 0
                        _F[k] |= true
                        P[k] = p[] 
                    end 
                end 
            end
        else # push
            _F .= false
            for j=_, k=_ 
                if F[j] && A[k, j] && !(V[k])
                    _F[k] |= true
                    P[k] <<choose(0)>>= j
                end 
            end 
        end 
        c = Scalar(0)
        @finch begin
            for k=_ 
                let _f = _F[k]
                    V[k] |= _f
                    c[] += _f
                end 
            end 
        end 
        (F, _F) = (_F, F)
        F_nnz = c[] 
    end 
    return P
end
\end{minted}
\subsection{GraphBLAS Breadth-First Search}
\begin{minted}{c}
//------------------------------------------------------------------------------
// LG_BreadthFirstSearch_SSGrB:  BFS using Suitesparse extensions
//------------------------------------------------------------------------------

>>>>

\section{Graph Algorithm Listings}\label{sec:graph_listings}

\subsection{Finch Breadth-First Search}
\begin{minted}{julia}
    function bfs_finch_kernel(edges, edgesT, source=5, alpha = 0.01)
    (n, m) = size(edges)
    edges = pattern!(edges)
    @assert n == m
    F = Tensor(SparseByteMap(Pattern()), n)
    _F = Tensor(SparseByteMap(Pattern()), n)
    @finch F[source] = true
    F_nnz = 1 
    V = Tensor(Dense(Element(false)), n)
    @finch V[source] = true
    P = Tensor(Dense(Element(0)), n)
    @finch P[source] = source
    while F_nnz > 0 
        if F_nnz/m > alpha # pull
            p = ShortCircuitScalar{0}()
            _F .= false
            for k=_ 
                if !V[k]
                    p .= 0
                    for j=_ 
                        if F[follow(j)] && AT[j, k]
                            p[] <<choose(0)>>= j
                        end 
                    end 
                    if p[] != 0
                        _F[k] |= true
                        P[k] = p[] 
                    end 
                end 
            end
        else # push
            _F .= false
            for j=_, k=_ 
                if F[j] && A[k, j] && !(V[k])
                    _F[k] |= true
                    P[k] <<choose(0)>>= j
                end 
            end 
        end 
        c = Scalar(0)
        @finch begin
            for k=_ 
                let _f = _F[k]
                    V[k] |= _f
                    c[] += _f
                end 
            end 
        end 
        (F, _F) = (_F, F)
        F_nnz = c[] 
    end 
    return P
end
\end{minted}
\subsection{GraphBLAS Breadth-First Search}
\begin{minted}{c}
//------------------------------------------------------------------------------
// LAGr_BreadthFirstSearch:  breadth-first search dispatch
//------------------------------------------------------------------------------

// Contributed by Scott McMillan, SEI Carnegie Mellon University

// Breadth-first-search via push/pull method if using SuiteSparse:GraphBLAS
// and its GxB extensions, or a push-only method otherwise.  The former is
// much faster.

// This is an Advanced algorithm.  SuiteSparse can use a push/pull method if
// G->AT and G->out_degree are provided.  G->AT is not required if G is
// undirected.  The vanilla method is always push-only.

#include "LG_alg_internal.h"

int LAGr_BreadthFirstSearch
(
    // output:
    GrB_Vector *level,
    GrB_Vector *parent,
    // input:
    const LAGraph_Graph G,
    GrB_Index src,
    char *msg
)
{

#if LAGRAPH_SUITESPARSE
    return LG_BreadthFirstSearch_SSGrB   (level, parent, G, src, msg) ;
#else
    return LG_BreadthFirstSearch_vanilla (level, parent, G, src, msg) ;
#endif
}

//------------------------------------------------------------------------------
// LG_BreadthFirstSearch_SSGrB:  BFS using Suitesparse extensions
//------------------------------------------------------------------------------
